Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-12 SupportingInformation.Rmd
saving model selection results for asym sensitivity

@@

@@

saveRDS(summary_stat,"./Results/asym_sens_results/beta_variation_summary_stat.RDS")
saveRDS(stat_npa_asym_beta_0.1_beta_0.9,"./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")
```

>>>>

ms_asym_beta_0.1_beta_0.9<-vector(mode = "list", length = 8) # initializing list to store model selection results for all possible beta variation
names(ms_asym_beta_0.1_beta_0.9)<-cname

@@

  ms_asym_beta_0.1_beta_0.9[[ic]]<-res

@@

saveRDS(summary_stat,"./Results/asym_sens_results/beta_variation_summary_stat.RDS")
saveRDS(ms_asym_beta_0.1_beta_0.9,"./Results/asym_sens_results/ms_asym_beta_0.1_beta_0.9.RDS")
saveRDS(stat_npa_asym_beta_0.1_beta_0.9,"./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")
```
